Supplementary Materials

### 2018-03-30 paper/application.tex
update discussion
change example in 6.2

%\shusen{Example where the prediction is correct but the alignment is wrong}
%%%% are we obtain correct prediction from wrong alignment %%%%%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
In the previous example, we show that the perfect alignment does not necessarily guarantee a correct prediction.
%
On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{break} and \textbf{sit} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. 
%These situations demonstrate the important of understanding the model decision making process, we can assess whether the model is behaving as intended.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most models will have a difficult time making correct inference.
%
The researchers start with a set of experiments they plan to run, from which, they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of with specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-ordinary behaviors in the model.
%
Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes, ensures a streamlined exploration experience that free the users from interruptions and tedious operations, allow them to focus on the more productive activities.

>>>>

%\shusen{Example where the prediction is correct but the alignment is wrong}
%%%% are we obtain correct prediction from wrong alignment %%%%%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. For the attention based NLI model, one underlying assumption is that the attention should capture the correct alignment between words in the premise and hypothesis sentence for the classifier to make an informed/correct decision.
In the previous example, we show that the perfect alignment does not necessarily guarantee a correct prediction.
%
On the flip side, we may produce the right predictions for the ``wrong'' reason (i.e., incorrect attention). 
As illustrated in Fig.~\ref{fig:wrongAlignRightPred}, the word \textbf{take} and \textbf{next} should not align with each other (Fig.~\ref{fig:wrongAlignRightPred}(a)), however, it still produce the correct \emph{neutral} label (Fig.~\ref{fig:wrongAlignRightPred}(b)).
%
%By looking into the model decision making process, we can assess whether the model is behaving as intended. 
%These situations demonstrate the important of understanding the model decision making process, we can assess whether the model is behaving as intended.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most models will have a difficult time making correct inference.
%
The researchers start with a set of experiments they plan to run, from which, they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of with specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-ordinary behaviors in the model.
%
